\documentclass[conference]{IEEEtran}
\usepackage{cite}  
\usepackage{graphicx}  
\usepackage{paralist} 
\usepackage{tabularx}    
\usepackage{url}       
\usepackage{balance}       
\usepackage{multirow}     
\usepackage{multicol}       
\usepackage[TABBOTCAP]{subfigure} 
\include{macro}                                           
                   
\begin{document}                             
                       
\title{Finding UUX Issues in User Reviews}
\author{\IEEEauthorblockN{  
E. Bakiu,
E. Guzman  
} 
\IEEEauthorblockA{Technische Universit\"at M\"unchen,
Garching, Germany} 
elsabakiu@gmail.com, emitza.guzman@mytum.de
}        
 
\newcommand{\etal}[0]{{{et al.}\ }}
\newcommand{\ie}[0]{{{i.e.}\ }} 
\maketitle
 
\begin{abstract}

%\boldmath 

\input{abstract_text}

\end{abstract}

% no keywords
         
\IEEEpeerreviewmaketitle  
      
\section{Introduction}  
\label{sec:intro}   
\input{introduction} 
      
\section{Approach}     
\label{sec:approach} 
\input{approach}      
         

\section{Evaluation Method}
\label{sec:Evaluation}
\input{evaluation}

\section{Evaluation Results} 
\label{sec:results}
\input{results}


%\section{Discussion}
%\label{sec:discussion}
%In this section we discuss the obtained results

\section{Discussion}
\label{sec:threats}
\input{discussion}

\section{Related Work}
\label{sec:related}
\input{related_work}

\section{Conclusions and Future Work}
\label{sec:conclusion}
\input{conclusions}

% use section* for acknowledgement
%\section*{Acknowledgment}
%The authors would like to thank...


% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}
 
% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
%\begin{thebibliography}{1}

%\end{thebibliography}
%\balance
%\bibliographystyle{IEEEtran}
%\bibliography{paper}  
     
     
\begin{thebibliography}{1}

\bibitem{paper:AntoniolICSME2008}
G.~Antoniol, K.~Ayari, M.~Di Penta, F.~Khomh, Y.~Guhneuc, \emph{Is it a bug or an enhancement?: a text-based approach to classify change requests}. CASCON, 2008:23.

\bibitem{paper:Bacchelli}
A. Bacchelli, T. Dal Sasso, M. D'Ambros, and M. Lanza. \emph{Content classification of development emails}. In Proceedings of the 34th International Conference on Software Engineering (ICSE), 2012, pp. 375-385. 

\bibitem{paper:Basili1996}
V. R.~Basili, L. C.~Briand, and W. L.~Melo, \emph{A validation of object oriented design metrics as quality indicators,} IEEE Trans. Software Eng., vol. 22, no. 10, pp. 751-761, 1996. 

\bibitem{paper:Bezerra2007}
M. Bezerra, A. L. I. Oliveira, and S. R. L. Meira, , \emph{A constructive rbf neural network for estimating the probability of defects in software modules,} in Neural Networks, 2007. IJCNN 2007. International Joint Conference on, 2007, pp. 2869-2874. 

\bibitem{paper:Blei2003}
D. M. ~Blei, A.Y. ~Ng, and M. I. ~Jordan, \emph{Latent dirichlet allocation}, in Journal of Machine Learning Research (JMLR), Vol. 3, 2003, pp. 993-1022.

\bibitem{paper:Cer2010}
D. Cer, M.C. de Marneffe, D. Jurafsky, and C.D. Manning, \emph{Parsing to Stanford dependencies: Trade-offs between speed and accuracy}, in Proceedings of the 7th International Conference on Language Resources and Evolution (LREC), 2010.

\bibitem{paper:Ceylan2006}
E. Ceylan, F. Kutlubay, and A. Bener, , \emph{Software defect identification using machine learning techniques,} in Software Engineering and Advanced Applications, 2006. SEAA ?06. 32nd EUROMICRO Conference on, 2006, pp. 240-247. 

\bibitem{paper:Chandy}
R. Chandy and H. Gu. \emph{Identifying spam in the iOS app store}. In Proceedings of the 2nd Joint WICOW/AIRWeb Workshop on Web Quality (WebQuality), 2012, pages 56-59.

\bibitem{paper:ARminer}
N.~Chen, J.~Lin, S.C.H.~Hoi, X.~Xiao, B.~Zhang, \emph{AR-miner: mining informative reviews for developers from mobile app marketplace}. In Proceedings of the 36th International Conference on Software Engineering (ICSE), 2014, pp. 767-778. 

\bibitem{paper:Chhetri2014}
Y. B. Chhetri and M. P. Robillard, \emph{Recommending Reference API Documentation}, in Empirical Software Engineering, 2014. To appear

\bibitem{paper:Dagan2005}
I. Dagan, O. Glickman, and B. Magnini,  \emph{The PASCAL recognizing textual entailment challenge}, in Proceedings of The First International Conference on Machine Learning Challenges: evaluating Predictive Uncertainly Visual Object Classification, and Recognizing Textual Entailment, 2005, pp. 177-190.

\bibitem{paper:deMarneffe2008}
M.C. de Marneffe, B. MacCartney, and C.D. Manning, , \emph{Generating typed dependency parses from phrase structure parses}, in Proceedings of LREC, 2006, pp. 449-454.

\bibitem{paper:Demsar2006}
J. Dem{\v s}ar,  \emph{Statistical comparisons of classifiers over multiple data sets}, in Journal of Machine Learning Research v.7, 2006, pp. 1-30.

\bibitem{paper:IR1992}
W. B.~Frakes and R.~Baeza-Yates, \emph{Information Retrieval: Data Structures and Algorithms?}. Prentice-Hall, Englewood Cliffs, NJ, 1992.

\bibitem{paper:Fu}
B. Fu, J. Lin, L. Li, C. Faloutsos, J. Hong, and N. Sadeh. \emph{Why people hate your app: Making sense of user feedback in a mobile app store.}. In Proc. of the International Conference on Knowledge Discovery and Data Mining (KDD), 2013, pages 1276-1284.

\bibitem{paper:Fundel2007}
K. Fundel, R. K\'"uffner, and R. Zimmer, \emph{RelEx - Relation extraction using dependency parse trees}, in Bioinformatics, v.23, n.3, 2007, pp. 365-371.

\bibitem{paper:Galvis}
L. V. Galvis Carreño and K. Winbladh. \emph{Analysis of user comments: an approach for software requirements evolution}. In Proceedings of the 2013 International Conference on Software Engineering (ICSE), 2013, pages 582-591. 

\bibitem{paper:Guzman}
E. ~Guzman, and W. ~Maalej \emph{How Do Users Like This Feature? A Fine Grained Sentiment Analysis of App Reviews}. In Proceedings of the 22nd IEEE International  Requirements Engineering Conference (RE), 2014, pp. 153-162

\bibitem{paper:Guzzi2013}
A. Guzzi, A. Bacchelli, M. Lanza, M. Pinzger, and A. van Deursen, 
\emph{Communication in open source software development mailing lists},
in Proceedings of the 10th Working Conference on Mining Software Repositories 
(MSR), 2013, pp 277-286. 

\bibitem{paper:Guzzi2012}
A. Guzzi, A. Begel, J.K. Miller, and K. Nareddy, 
\emph{Facilitating Enterprise Software Developer Communication with CARES},
in Proceedings of the 34th International Conference on Software Engineering 
(ICSE), 2012, pp 1367-1370. 

\bibitem{paper:Harman}
M. Harman, Y. Jia, and Y. Zhang. \emph{App store mining and analysis: MSR for app stores.} In Proc. of the Working Conference on Mining Software Repositories (MSR) 2012, pages 108-111.

\bibitem{paper:Iacob}
C. Iacob and R. Harrison. \emph{Retrieving and analyzing mobile apps feature requests from online reviews}. In Proc. of the Working Conference on Mining Software Repositories (MSR), 2013, pages 41-44.

\bibitem{paper:Kucuktunc}
O. Kucuktunc, B. B. Cambazoglu, I. Weber, and H. Ferhatosmanoglu. \emph{A large-scale sentiment analysis for Yahoo! Answers}, In Proceedings of the International Conference on Web Search and Data Mining (WSDM), 2012, pp 633-642.

\bibitem{paper:Li}
H. Li, L. Zhang, L. Zhang, and J. Shen. \emph{A user satisfaction analysis approach for software evolution}. In Proc. of the Progress in Informatics and Computing Conference (PIC), 2010, volume 2, pages 1093-1097.

\bibitem{paper:Liu2010}
Y. Liu, T. M. Khoshgoftaar, and N. Seliya, , \emph{Evolutionary optimization of software quality modeling with multiple repositories,} IEEE Trans. Softw. Eng., vol. 36, no. 6, Nov. 2010, pp. 852-864. 

\bibitem{paper:Nivre2010}
J. Nivre, L. Rimell, R. McDonald, and C. G\'omez-Rodr\'iguez, \emph{Evaluation of dependency parsers on unbounded dependencies}, in Proceedings of COLING, 2010, pp. 813-821.

\bibitem{paper:Pagano}
D.~Pagano, and W.~Maalej \emph{User Feedback in the AppStore: An Empirical Study}. In Proceedings of the 21st IEEE International Requirements Engineering Conference (RE), 2013, pp.125-134.

\bibitem{paper:Pandita2012}
R. Pandita, X.Xiao, H. Zhong, and T. Xie, \emph{Inferring method specifications from natural language API descriptions}, in Proceedings of the 34th International Conference on Software Engineering (ICSE), 2012, pp. 815-825

\bibitem{paper:Pang}
B. Pang, L. Lee,  and S. Vaithyanathan,  \emph{Thumbs up?: sentiment classification using machine learning techniques}, Proceedings of the ACL-02 Conference on Empirical Methods in Natural Language Processing, pp. 79-86, 2002.

\bibitem{paper:Panichella2012}
S. Panichella, J. Aponte, M. Di Penta, A. Marcus, and G. Canfora \emph{Mining source code descriptions from developers communications}, in Proceedings of the 20th IEEE International Conference on Program Comprehension, 2012, pp. 63-72.

\bibitem{paper:Slankas2014}
J. Slankas, X. Xiao, L. Williams, and T. Xie, \emph{Relation extraction for inferring access control rules from natural language artifacts}, in Proceedings of the 30th Annual Computer Security Applications Conference (ACSAC), 2014, pp. 366-375.

\bibitem{paper:ML2005}
I.~Witten and E.~Frank, \emph{Data Mining: Practical Machine Learning Tools and Techniques}. Morgan Kaufmann, 2005. 

\bibitem{paper:ZhouText2014} 
Y. ~Zhou, Y.~Tong, R.~Gu, H.~Gall, \emph{Combining Text Mining and Data Mining for Bug Report Classification?}. In Proceeding of 30th International Conference on Software Maintenance and Evolution (ICSME), 2014, pp. 311-320.

\bibitem{paper:Zimmermannesem2009}
T. Zimmermann and N. Nagappan, , \emph{Predicting defects with program dependencies}, in Empirical Software Engineering and Measurement, 2009. ESEM 2009. 3rd International Symposium on, 2009, pp. 435-438. 


%\bibitem{paper:Kaur}
%A. ~Kaur, Er. ~Nidhi Gumber \emph{A Review on Sentimental Analysis of Application %Reviews}. In International Journal of Modern Engineering Research (IJMER), Vol 4, Iss. 6, %June 2014. pp. 72-76.
 
%\bibitem{paper:Sentiwordnet}
%A. ~Esuli, and F. ~Sebastiani \emph{SentiWordNet: A publicly available lexical resource for opinion mining}. In Proceedings of %Language Resources and Evaluation Confernce (LREC), 2006, pp. 417-422.

%\bibitem{paper:Hamouda}
%A.~Hamouda, and A.~Rohaim \emph{Reviews Classification Using SentiWordNet Lexicon}. in Journal on Computer Science and %Information Technology (OJCSIT), Vol. (2), No.(1), 2011. 


\end{thebibliography}
		    
\end{document}







